---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hillysilly

<!-- badges: start -->
<!-- badges: end -->

The goal of hillysilly is to plot elevation very uselessly for a set of input addresses or locations. 

## Installation

You can install the development version of hillysilly like so:

``` r
remotes::install_github("mdsumner/hillysilly")
```


## TODO

- remove raster (but update anglr too)
- cleanup messy code
- cleanup bad use of rgl window control
- fix spacing/offset when different tile dimensions or width/height are used!
- provide colour control
- expand on tile logic (and the matrix of inputs possible)
- allow other input data, other raster sources 
- etc


## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE}
library(hillysilly)
## basic example code
hillysilly(c("Auckland", "Murray Hill",  "Zurich", "Oxford"))
```

![alt text][snapshot3d_01]

[snapshot3d_01]: man/figures/snapshot3d_01.png "Four cities"

